Bridging [TBD]

### 2014-03-17 paper/draft.tex
Added Related Works paragraph
Premier abstract
Extraction du problème, de la contrib et de l'implem
Il faut intégrer le commentaire au-dessus (notamment le trade-off qui
n'apparait pas).

\title{}

@@

\abstract{
%Today, hypervisors have to find a complex trade-off between functionalities provided and security assurance. Those requirements are contrasting by design:
%adding new features will generally increases the LoC and consequently the attack surface. On the contrary, those code additions are required to properly fulfill market requests. 
%
%Nested virtualization is a technique capable to diversify hypervisor features. Exploiting an extra layer of virtualization, we will be able to decouple different requirements, avoiding the need to find delicate trade-off.
%
%In this paper, we will analyze the state of nested virtualization in modern hypervisor and evaulating the impact of utilization of microhypervisor to enforce a stronger security level.
}

>>>>

\title{ Bridging [TBD]}

@@

\abstract{
%Today, hypervisors have to find a complex trade-off between functionalities provided and security assurance. Those requirements are contrasting by design:
%adding new features will generally increases the LoC and consequently the attack surface. On the contrary, those code additions are required to properly fulfill market requests. 
%
%Nested virtualization is a technique capable to diversify hypervisor features. Exploiting an extra layer of virtualization, we will be able to decouple different requirements, avoiding the need to find delicate trade-off.
%
%In this paper, we will analyze the state of nested virtualization in modern hypervisor and evaulating the impact of utilization of microhypervisor to enforce a stronger security level.
The problem of homogeneity over multiple IaaS providers is receiving considerable attention with the evolution toward nested virtualization. These new architectures unveil user-centric opportunities such as efficient resources management and VM migration. However the inherent drawbacks hinder its global adoption with a larger TCB and the complexity to monitor another virtualization layer. Thus, we argue that the promising architectural view of micro hypervisors approach is the key to the separation of hypervisor duties and reducing the attack surface.

Furthermore, our architecture mushrooms commodity and micro hypervisors to leverage nested virtualization in terms of user-data privacy, modularity, TCB size and compatibility. These design principles are evaluated for each architecture configuration and compared to establish a reference security architecture. The resulting combination is built over common hypervisors empowered with micro hypervisors features. A reference implementation proven the architecture to be viable and will be extended to meet broader hypervisor scopes, enabling migration over heterogeneous cloud servers.
}
